---
title: "p8105_hw5_ga2612"
author: "Lupe Antonio"
date: "11/12/2023"
output: 
  github_document:
    toc: TRUE
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Problem 1

```{r, message = FALSE}
#loading data
homicide_data <- read_csv('data_hw5/homicide_data.csv')
```







## Problem 2

data from a longitudinal study that included a control arm and an experimental arm. Data for each participant is included in a separate file, and file names include the subject ID and arm.

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:

Start with a dataframe containing all file names; the list.files function will help (DONE)


Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe


Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary
Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.



```{r}
#loading data
file_names <- list.files(path = 'data_hw5/p2_data') %>%
  as_tibble() %>%
  rename(file_name = value) %>%
  #iterating over file names, reading file, and create new variable in df
  mutate(
    
  )
  
```

```{r}
#iterating over file names
purrr::map(file_names$file_name, read_csv)
```

