---
title: "p8105_hw5_ga2612"
author: "Lupe Antonio"
date: "11/12/2023"
output: 
  github_document:
    toc: TRUE
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(purrr)
library(broom)
library(ggplot2)
```

## Problem 1

```{r, message = FALSE}
#loading data
homicide_data <- read_csv('data_hw5/homicide_data.csv')
```







## Problem 2

```{r, message=FALSE}
#loading data
file_names <- list.files(path = 'data_hw5/p2_data') %>%
  as_tibble() %>%
  rename(file_name = value) %>%
  #iterating over file names, reading file, and create new variable in df
  mutate(
    data = map(str_c('./data_hw5/p2_data/', file_name), read_csv)) %>%
  unnest(cols = data) %>%
  pivot_longer(week_1:week_8,
               names_to = 'week',
               values_to = 'value') %>%
  mutate(
    #creating arm variable for either control or experimental
    arm = case_when(
      str_detect(file_name, 'con') ~ 'control',
      TRUE ~ 'experimental'),
    
    #creating subject id variable
    id = as.numeric(str_sub(file_name, start = 5, end = 6)),
    
    #updating week to numeric
    week = as.numeric(str_sub(week, start = 6, end = 6)))
  
```


```{r}
#creating plot
file_names %>%
  ggplot(aes(x = week, y = value, color = arm, group = interaction(id, arm))) +
  geom_line() +
  ggtitle('Observations per subjects between week 1 and 8')
```

Based on the plot above, we can see that over time the participants with the experimental arm had increasing values over time. While those with the control arm had relatively consistent values over time, not much fluctuation. 


## Problem 3

Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of μ on the x axis. Describe the association between effect size and power.

Make a plot showing the average estimate of μ̂ on the y axis and the true value of μ on the x axis. 

Make a second plot (or overlay on the first) the average estimate of μ̂ only in samples for which the null was rejected on the y axis and the true value of μ on the x axis. Is the sample average of μ̂ across tests for which the null is rejected approximately equal to the true value of μ? Why or why not?

```{r}
sim_mean_pval <- function(mean, n = 30,sigma = 5){
  sim_data = tibble(
    x = rnorm(n = n, mean = 0, sd = sigma))
  
  mean_pval = sim_data %>%
    pull(x) %>%
    #.95 for conf.level, 0 mu is already preset. 
    t.test() %>%
    tidy() %>%
    select(estimate, p.value)
  
  return(mean_pval)}
```

```{r}
#df for all iterations
sim_results_df <- expand_grid(
  iter = 1:5000,
  alternate_mus = c(1, 2, 3, 4, 5, 6)) %>%
  mutate(
    values_df = map(alternate_mus, sim_mean_pval)) %>%
  unnest(values_df)
```

Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of μ on the x axis. Describe the association between effect size and power. 
```{r}
sim_results_df %>%
  mutate(power = case_when(
      p.value < 0.05 ~ 1,
      TRUE ~ 0)) %>%
  group_by(alternate_mus) %>%
  ggplot()
```

```{r}
sim_results_df %>%
  group_by(alternate_mus) %>%
  summarize(power = mean(p.value < 0.05)) %>%
  ggplot(aes(x = alternate_mus, y = power)) +
  geom_point()
```





Make a plot showing the average estimate of μ̂ on the y axis and the true value of μ on the x axis.
```{r}
sim_results_df %>%
  group_by(alternate_mus) %>%
  mutate(average_mu_values= mean(estimate)) %>%
  ggplot(aes(x = alternate_mus, y = average_mu_values)) +
  geom_point() +
  xlab('True mu values') +
  ylab('Average mu values') +
  ggtitle('Average estimated of mu_hat per true values of mu')
```

Make a second plot (or overlay on the first) the average estimate of μ̂ only in samples for which the null was rejected on the y axis and the true value of μ on the x axis.
```{r}

```


